---
title: "Homework1"
author: "Xinyu Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Homework1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Question 1

Use knitr to produce an example in the book which contains at least one figure.

## Answer 1

Use lattice package to compare the ECDF and CDF of random data from normal distribution. 
```{r}
library(lattice)
n <- seq(20, 50, 10)
x <- rnorm(sum(n))
y <- factor(rep(n, n), labels=paste("n =", n))
densityplot(~ x | y,
panel = function(x, ...) {
panel.densityplot(x, col="red", ...)
panel.mathdensity(dmath=dnorm,
args=list(mean=mean(x), sd=sd(x)),
col="darkblue")
})
```

The larger the sample size, the better the fitting effect.

## Question 2

Use knitr to produce an example in the book which contains at least one table.

## Answer 2

Use linear Regression to fit data.
```{r}
x1<-c(0.10, 0.11, 0.12, 0.13, 0.14, 0.15,
0.16, 0.17, 0.18, 0.20)
x2<-c(1,2,3,4,5,5,4,3,2,1)
y<-c(42.0, 43.5, 49.0, 45.5, 45.0, 47.5,
49.0, 53.0, 53.0, 55.0)
lm.sol<-lm(y ~ x1+x2)
knitr::kable(summary(lm.sol)$coef)
```


## Question 3

Use knitr to produce an example in the book which contains at least a couple of Latex formulas.

## Answer 3

Pdf of multivariate normal distribution:
$$f_{\mathbf{x}}\left(x_{1}, \ldots, x_{k}\right)=\frac{1}{\sqrt{(2 \pi)^{k}|\mathbf{\Sigma}|}} \exp \left(-\frac{1}{2}(\mathbf{x}-\boldsymbol{\mu})^{\mathrm{T}} \mathbf{\Sigma}^{-1}(\mathbf{x}-\boldsymbol{\mu})\right)$$