---
title: "intro2"
author: "Xinyu Li"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(StatComp20058)
```

##  _myst_  and  _mean_ci_

```{r message=FALSE}
data("data")
attach(data)
myst(age)
```
This function has a preliminary understanding of a sample set by calculating basic statistics such as mean value, variance, skewness, kurtosis, etc., which is similar to the simplified SumMAR function.



```{r message=FALSE, warning=FALSE}
data("data")
attach(data)
mean_ci(age,0.95)
```
This function can output a confidence interval of the specified confidence degree of an approximate normal distribution, which is applicable in the case of large samples

## _getRandomNum_ and _outlierKD_

```{r}
z = getRandomNum(x = 5,min = 2230,q25 = 18123,q50 = 52213,q75 = 78312,max = 234234123)
quantile(z)
fivenum(z)
```

According to order statistics, random sequences can be generated, and some statistical studies on order statistics can be carried out


```{r fig.height=30, fig.width=30, include=FALSE}
data("data")
attach(data)
par(mfrow=c(4,1),mar=rep(0,4))
outlierKD(data,age)
```

Outliers are detected for a sequence and the decision is made whether to delete or convert them to missing values




