---
title: "Homework7"
author: "Xinyu Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Homework7}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### question
Exercise 8.3 (page 243, Statistical Computating with R).
Design experiments for evaluating the performance of the NN,

### answer
#### **Exercise 8.3**
The Count 5 test for equal variances in Section 6.4 is based on the maximum number of extreme points. Example 6.15 shows that the Count 5 criterion is not applicable for unequal sample sizes. Implement a permutation test for equal variance based on the maximum number of extreme points that applies when sample sizes are not necessarily equal.

##### solution:
```{r}
library(boot)
library(energy)
library(MASS)
set.seed(1234)
maxout <- function(x, y) {
  X <- x - mean(x)
  Y <- y - mean(y)
  outx <- sum(X > max(Y)) + sum(X < min(Y))
  outy <- sum(Y > max(X)) + sum(Y < min(X))
  return(max(c(outx, outy))) 
}
n1 <-20
n2 <-30
mu1 <- 1
mu2 <- 4
sigma1 <-1 
sigma2 <- 6
x <- rnorm(n1, mu1, sigma1)
y <- rnorm(n2, mu2, sigma2)
d0<-maxout(x, y)
R <- 999 #number of replicates
z <- c(x, y) #pooled sample
K <- 1:50
reps <- numeric(R) #storage for replicates
for (i in 1:R) {
  k <- sample(K, size = 10, replace = FALSE)
  x1 <- z[k]
  y1 <- z[-k] #complement of x1
  reps[i] <- maxout(x1, y1)
}
p <- mean(c(d0, reps) >= d0)
p
```
It can be seen from the results: 0.026<0.05, which means that the null hypothesis is rejected at this level of significance, indicating that it comes from two different distributions, and it also corrects and improves the shortcomings of the different samples of Count 5 test.
```{r}
hist(reps, breaks = "scott",main = "Histogram",xlab = "a",col="black")
points(d0, 0, cex = 1, pch = 16,col="red")
```

#### **Exercise 1**
Design experiments for evaluating the performance of the NN,energy, and ball methods in various situations.
##### solution:
I Unequal variances and equal expectations:
variances= 2 and 1,expectations=0
```{r}
library(Ball)
library(RANN)
```
```{r}
Tn <- function(z, ix, sizes,k) {
  n1 <- sizes[1]; n2 <- sizes[2]; n <- n1 + n2
  if(is.vector(z)) z <- data.frame(z,0);
  z <- z[ix, ];
  NN <- nn2(data=z, k=k+1) # what's the first column?
  block1 <- NN$nn.idx[1:n1,-1]
  block2 <- NN$nn.idx[(n1+1):n,-1]
  i1 <- sum(block1 < n1 + .5); i2 <- sum(block2 > n1+.5)
  (i1 + i2) / (k * n)
}
m <- 1e3; k<-3; p<-2;set.seed(12345)
n1 <- n2 <- 50; R<-999; n <- n1+n2; N = c(n1,n2)
eqdist.nn <- function(z,sizes,k){
  boot.obj <- boot(data=z,statistic=Tn,R=R,
                   sim = "permutation", sizes = sizes,k=k)
  ts <- c(boot.obj$t0,boot.obj$t)
  p.value <- mean(ts>=ts[1])
  list(statistic=ts[1],p.value=p.value)
}
p.values <- matrix(NA,m,3)
for(i in 1:m){
  x <- matrix(rnorm(n2*p,0,2),ncol=p);
  y <- cbind(rnorm(n2,0,2),rnorm(n2,0,1));
  z <- rbind(x,y)
  p.values[i,1] <- eqdist.nn(z,N,k)$p.value
  p.values[i,2] <- eqdist.etest(z,sizes=N,R=R)$p.value
  p.values[i,3] <- bd.test(x=x,y=y,num.permutations=999,seed=i*12345)$p.value
}
```
```{r}
alpha <- 0.05;
pow <- colMeans(p.values<alpha)
matrix(pow, nrow=1,dimnames=list("power", c("eqdist.nn","eqdist.etest","bd.test")))
```
The power of bd.test is better.

II Unequal variances and unequal expectations:
variances=  1,expectations= 0 and 1
```{r}
library(Ball)
library(RANN)
```
```{r}
Tn <- function(z, ix, sizes,k) {
  n1 <- sizes[1]; n2 <- sizes[2]; n <- n1 + n2
  if(is.vector(z)) z <- data.frame(z,0);
  z <- z[ix, ];
  NN <- nn2(data=z, k=k+1) # what's the first column?
  block1 <- NN$nn.idx[1:n1,-1]
  block2 <- NN$nn.idx[(n1+1):n,-1]
  i1 <- sum(block1 < n1 + .5); i2 <- sum(block2 > n1+.5)
  (i1 + i2) / (k * n)
}
m <- 1e3; k<-3; p<-2;set.seed(12345)
n1 <- n2 <- 50; R<-999; n <- n1+n2; N = c(n1,n2)
eqdist.nn <- function(z,sizes,k){
  boot.obj <- boot(data=z,statistic=Tn,R=R,
                   sim = "permutation", sizes = sizes,k=k)
  ts <- c(boot.obj$t0,boot.obj$t)
  p.value <- mean(ts>=ts[1])
  list(statistic=ts[1],p.value=p.value)
}
p.values <- matrix(NA,m,3)
for(i in 1:m){
  x <- matrix(rnorm(n2*p),ncol=p);
  y <- cbind(rnorm(n2,0,1),rnorm(n2,1,1));
  z <- rbind(x,y)
  p.values[i,1] <- eqdist.nn(z,N,k)$p.value
  p.values[i,2] <- eqdist.etest(z,sizes=N,R=R)$p.value
  p.values[i,3] <- bd.test(x=x,y=y,num.permutations=999,seed=i*12345)$p.value
}
```

```{r}
alpha <- 0.05;
pow <- colMeans(p.values<alpha)
matrix(pow, nrow=1,dimnames=list("power", c("eqdist.nn","eqdist.etest","bd.test")))
```
The power of bd.test is better.


III Non-normal distributions: t distribution with 1 df (heavy-taileddistribution), bimodel distribution (mixture of two normal distributions)

```{r}
Tn <- function(z, ix, sizes,k) {
  n1 <- sizes[1]; n2 <- sizes[2]; n <- n1 + n2
  if(is.vector(z)) z <- data.frame(z,0);
  z <- z[ix, ];
  NN <- nn2(data=z, k=k+1) # what's the first column?
  block1 <- NN$nn.idx[1:n1,-1]
  block2 <- NN$nn.idx[(n1+1):n,-1]
  i1 <- sum(block1 < n1 + .5); i2 <- sum(block2 > n1+.5)
  (i1 + i2) / (k * n)
}
m <- 1e3; k<-3; p<-2;set.seed(12345)
n1 <- n2 <- 50; R<-999; n <- n1+n2; N = c(n1,n2)
Sigma <- matrix(c(1,0.1,0.1,1),2,2)
eqdist.nn <- function(z,sizes,k){
  boot.obj <- boot(data=z,statistic=Tn,R=R,
                   sim = "permutation", sizes = sizes,k=k)
  ts <- c(boot.obj$t0,boot.obj$t)
  p.value <- mean(ts>=ts[1])
  list(statistic=ts[1],p.value=p.value)
}
p.values <- matrix(NA,m,3)
for(i in 1:m){
  x <- matrix(rt(n2*p,1),ncol=p);
  y <- mvrnorm(n=n2, rep(0,2), Sigma);
  z <- rbind(x,y)
  p.values[i,1] <- eqdist.nn(z,N,k)$p.value
  p.values[i,2] <- eqdist.etest(z,sizes=N,R=R)$p.value
  p.values[i,3] <- bd.test(x=x,y=y,num.permutations=999,seed=i*12345)$p.value
}
```


```{r}
alpha <- 0.05;
pow <- colMeans(p.values<alpha)
matrix(pow, nrow=1,dimnames=list("power", c("eqdist.nn","eqdist.etest","bd.test")))
```

The power of eqdist.etest is better. Ball could be more powerful for non-location family distribution

IIII Unbalanced samples (say, 1 case versus 10 controls)：n1=50,n2=500
```{r}
Tn <- function(z, ix, sizes,k) {
  n1 <- sizes[1]; n2 <- sizes[2]; n <- n1 + n2
  if(is.vector(z)) z <- data.frame(z,0);
  z <- z[ix, ];
  NN <- nn2(data=z, k=k+1) # what's the first column?
  block1 <- NN$nn.idx[1:n1,-1]
  block2 <- NN$nn.idx[(n1+1):n,-1]
  i1 <- sum(block1 < n1 + .5); i2 <- sum(block2 > n1+.5)
  (i1 + i2) / (k * n)
}
m <- 1e3; k<-3; p<-2;set.seed(12345)
n1 <- 20
n2 <- 200; R<-999; n <- n1+n2; N = c(n1,n2)
Sigma <- matrix(c(1,0.1,0.1,1),2,2)
eqdist.nn <- function(z,sizes,k){
  boot.obj <- boot(data=z,statistic=Tn,R=R,
                   sim = "permutation", sizes = sizes,k=k)
  ts <- c(boot.obj$t0,boot.obj$t)
  p.value <- mean(ts>=ts[1])
  list(statistic=ts[1],p.value=p.value)
}
p.values <- matrix(NA,m,3)
for(i in 1:m){
  x <- matrix(rnorm(n1*p),ncol=p);
  y <- matrix(rnorm(n2*p),ncol=p);
  z <- rbind(x,y)
  p.values[i,1] <- eqdist.nn(z,N,k)$p.value
  p.values[i,2] <- eqdist.etest(z,sizes=N,R=R)$p.value
  p.values[i,3] <- bd.test(x=x,y=y,num.permutations=999,seed=i*12345)$p.value
}
```

```{r}
alpha <- 0.1;
pow <- colMeans(p.values<alpha)
matrix(pow, nrow=1,dimnames=list("power", c("eqdist.nn","eqdist.etest","bd.test")))
```
It can be seen that for unbalanced samples, the efficacy of the three is not very good