---
title: "Homework10"
author: "Xinyu Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Homework10}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### question
1.Write an Rcpp function for Exercise 9.4 (page 277, Statistical
Computing with R).

2.Compare the corresponding generated random numbers with
those by the R function you wrote before using the function
“qqplot”.

3 Campare the computation time of the two functions with the
function “microbenchmark”.



### answer
#### **Exercise 9.4**
Implement a random walk Metropolis sampler for generating the standard Laplace distribution (see Exercise 3.2). For the increment, simulate from a normal distribution. Compare the chains generated when different variances are used for the proposal distribution. Also, compute the acceptance rates of each chain

##### solution:
```{r}
library(StatComp20058)
x0<-25
sigma<-c(0.05,1,2,16)
N<-3000
M1=MetropolisC(sigma[1],x0,N)
M2=MetropolisC(sigma[2],x0,N)
M3=MetropolisC(sigma[3],x0,N)
M4=MetropolisC(sigma[4],x0,N)
acceptanceC<-1-c(M1[[2]][1],M2[[2]][1],M3[[2]][1],M4[[2]][1])/N
index<-1:2000
My1<-M1[[1]][index]
My2<-M2[[1]][index]
My3<-M3[[1]][index]
My4<-M4[[1]][index]
opar<-par(no.readonly = T)
par(mar = c(4,3,1,1)+0.1)
plot(index,My1,type = "l",xlab = "sigma=0.05")
plot(index,My2,type = "l",xlab = "sigma=1")
plot(index,My3,type = "l",xlab = "sigma=2")
plot(index,My4,type = "l",xlab = "sigam=16")
```

#### **question 2**
.Compare the corresponding generated random numbers with
those by the R function you wrote before using the function
“qqplot”.

##### solution:
```{r}
library(StatComp20058)
MM1=MetropolisR(sigma[1],x0,N)
MM2=MetropolisR(sigma[2],x0,N)
MM3=MetropolisR(sigma[3],x0,N)
MM4=MetropolisR(sigma[4],x0,N)
acceptanceR<-1-c(M1$k,M2$k,M3$k,M4$k)/N
list(acceptanceC=acceptanceC,acceptanceR=acceptanceR)
opar<-par(no.readonly = T)
par(mar = c(4,3,1,1)+0.1)
qqplot(M1[[1]],MM1$x)
qqplot(M2[[1]],MM2$x)
qqplot(M3[[1]],MM3$x)
qqplot(M4[[1]],MM4$x)
```

#### **question 3**
Campare the computation time of the two functions with the
function “microbenchmark”.


##### solution:
```{r}
library(microbenchmark)
library(StatComp20058)
tS1<-microbenchmark(MC=MetropolisC(sigma[1],x0,N),MR=MetropolisR(sigma[1],x0,N))
tS2<-microbenchmark(MC=MetropolisC(sigma[2],x0,N),MR=MetropolisR(sigma[2],x0,N))
tS3<-microbenchmark(MC=MetropolisC(sigma[3],x0,N),MR=MetropolisR(sigma[3],x0,N))
tS4<-microbenchmark(MC=MetropolisC(sigma[4],x0,N),MR=MetropolisR(sigma[4],x0,N))
TI1<-summary(tS1)
TI2<-summary(tS2)
TI3<-summary(tS3)
TI4<-summary(tS4)
```


```{r}
print(TI1)
```


```{r}
print(TI2)
```


```{r}
print(TI3)
```

```{r}
print(TI4)
```
C++ is much efficient than R is several orders of magnitude faster. 
